
%====================
% EXPERIENCE A
%====================
\subsection{{Electronics Design Engineer \hfill May 2025 --- Present}}
\subtext{AP-FLYER \hfill Warsaw}

\begin{zitemize}
    \item I designed digital-analog circuits for unmanned airial vechicles for governmental agencies and the military.
    \item I wrote software in C language for STM32 microcontrollers managing avionics, power supply, and self-guidance systems of UAV.
    \item I assembled and tested the designed electronic components, ensuring their compliance with strict technical requirements.
    \item I worked with an interdisciplinary team, including mechanical engineers and programmers, to ensure the integration of electronic systems with the aerospace platform.
\end{zitemize}

%====================
% EXPERIENCE B
%====================

\subsection{{Electronics Design Engineer \hfill November 2024 --- Present}}
\subtext{Czaki Thermo-Product \hfill Warsaw}
\begin{zitemize}
    \item Designed a precision humidity and temperature transducer based on capacitive polymer humidity sensors, achieving a resolution below 3fF.
    \item Programmed an MSP430 microcontroller for data processing and sensor calibration, implementing communication via MODBUS and a 4-20mA current loop, allowing integration with standard control systems.
\end{zitemize}

% ====================
% EXPERIENCE C
%====================

\subsection{{R\&D Electronics Engineer \hfill July 2023 --- October 2024}}
\subtext{SVANTEK \hfill Warsaw}

\begin{zitemize}
    \item Designed the architecture for an automated module tester based on Raspberry Pi 5 and FPGA (Xilinx Artix-7), integrated with dedicated, in-house developed hardware, significantly shortening module bring-up-time.
    \item Developed the tester control software in C++, Rust, and Go, including a custom I2C slave driver for the RP1 chip \\ (in C), enabling EEPROM memory emulation working as a slave.
    \item Created an intuitive user interface (UI) in Python, automating the testing process by fetching tests from a server, executing them, and reporting the results, thereby eliminating the need for manual execution.
\end{zitemize}

%====================
% EXPERIENCE C
%====================

% \subsection{{KYC Specialist, Operational Support Department \hfill June 2020 --- September 2022}}
% \subtext{XTB Brokers S.A. \hfill Warsaw}
% 
% \begin{zitemize}
% \item Worked within the KYC operational support team, verifying client documentation in accordance with AML/KYC regulations, ensuring compliance with legal regulations across various jurisdictions.
% \item Collaborated effectively within a dynamic international financial environment, working closely with a multilingual team to provide high-quality support.
% \end{zitemize}
% 
%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: "../resume_en"
%%% End:
